Source Code Volatility Metric

### 2020-04-17 paper/article.tex
cite

...

@@

\begin{align}
G &= [g_1, g_2, \dots, g_{Z}] \\
\delta &= ( \check{T} - \hat{T} ) / Z \\
g_j &= \sum_{i=1}^N [ j(\delta-1) < t_i < j\delta ]
\end{align}

@@

The Figure~\ref{fig:3} demonstrates the relationship between
the logarithm of the size of the Git repository in bytes~($M_3$) and
the logarithm of its volatility~($V$).
It is visually obvious that
repositories with more directories tend to have higher values
of the volatility metric.

\begin{figure}[h]
  \input{dirs.tex}
  \caption{The relationship between the number of repositories in the repository and its volatility}
  \label{fig:3}
\end{figure}

>>>>

There are a few existing code change metrics, including code churn~\citep{munson1998}
and others~\citep{fentonsoftware}.

@@

\begin{align}
\delta &= ( \check{T} - \hat{T} ) / Z \\
G &= [g_1, g_2, \dots, g_{Z}] \\
g_j &= \sum_{i=1}^N [ j(\delta-1) < t_i < j\delta ]
\end{align}

@@

\section{Discussion}

It was demonstrated that the size of the source code is an important
factor negatively affecting maintainability and other quality characteristicts.
For example, \citep{heitlager2007} suggested to consider ``volume'' (the amount of code
in the repository) as a primary contributor to an aggregate maintainability index
of a software because ``it is fairly intuitive that the total size of a system should
feature heavily in any measure of maintainability.''
